### 2024-02-22 docs/manuscript/manuscript.qmd
Cambios menores: -N añadido al abstract y Participants -Limitación añadida a discusión

**Background**: Physical fitness, body composition, and the autonomic response to exercise are important predictors of health-related outcomes in older adults, but their interplay is not fully understood, therefore, this study aims to assess the associations between these variables and possible mediating effects. **Methods**: an observational cross-sectional study was conducted in XX community-dwelling older people, recruited by non-probabilistic sampling. To obtain body composition parameters, a bio-impedance analysis was made, then, the Short Physical Performance Battery (SPPB) was used to assess physical fitness, and the Heart Rate Variability (HRV) was recorded before, during and after the Two-Minute Step Test (TMST), to assess cardiac autonomic response to physical exercise. Geriatric depression and anxiety symptoms were assessed as secondary measures. Correlation and mediating effects analyses were carried out. **Results**: SPPB score was negatively related to body fat percentage (r = -0.273, p = 0.015), but positively related to SNS index during exercise (r = 0.313, p = 0.006). Also, a negative link existed between body fat and sympathetic activity: SNS index (r = -0.252, p = 0.030) and Stress index (r = 0.258, p = 0.027) during TMST. But a positive link with parasympathetic activity: RMSSD (r = 0.253, p = 0.029) and SDNN (r = 0.269, p = 0.020) **Conclusion**: the findings unveil a triangular relationship, where body fat percentage significantly impacts physical fitness and cardiac autonomic activity during exercise, while a greater sympathetic activity correlates with higher physical fitness. Additionally, physical fitness moderates the link between body fat and cardiac autonomic activity, emphasizing its importance for older adults' health. Further research is needed to explore psychological variables' moderating effects.

@@

XX community-dwelling older adults were recruited and selected by non-probabilistic sampling, from the Region of Magallanes and Chilean Antartica, Chile. They were included if: 65 years age or older; residents of the Region of Magallanes and Chilean Antartica, Chile; and being able to understand the study aims and instructions. But they were excluded in case of: diagnosis of congenital heart disease; consumption of beta-blocker drugs, taking stimulant substances within 24 h before assessments session; motor or cognitive disability; inability to understand instructions or written content; or presence of pain during cardiac or physical assessments.

@@

In addition to the potential strengths of this cross-sectional study, it is not without limitations. In first place, our study design prevents us from making objective inferences about the direction of the relationships, highlighting the relevance of longitudinal research exploring causal relations between our variables and underlying mechanisms. In second place, a relatively small sample was included, limiting generalizability and statistical power of the analysis. It should also be noted that the relationships between physical fitness and cardiac autonomic response to exercise were not made within the same instrument, due to the possible lack of SPPB to generate an adequate physical stress, and of TMST to inform general physical fitness of the participants. Further research could investigate the impact of cardiac autonomic response on performance during the same task, in this age group.

>>>>

**Background**: Physical fitness, body composition, and the autonomic response to exercise are important predictors of health-related outcomes in older adults, but their interplay is not fully understood, therefore, this study aims to assess the associations between these variables and possible mediating effects. **Methods**: an observational cross-sectional study was conducted in 81 community-dwelling older people, recruited by non-probabilistic sampling. To obtain body composition parameters, a bio-impedance analysis was made, then, the Short Physical Performance Battery (SPPB) was used to assess physical fitness, and the Heart Rate Variability (HRV) was recorded before, during and after the Two-Minute Step Test (TMST), to assess cardiac autonomic response to physical exercise. Geriatric depression and anxiety symptoms were assessed as secondary measures. Correlation and mediating effects analyses were carried out. **Results**: SPPB score was negatively related to body fat percentage (r = -0.273, p = 0.015), but positively related to SNS index during exercise (r = 0.313, p = 0.006). Also, a negative link existed between body fat and sympathetic activity: SNS index (r = -0.252, p = 0.030) and Stress index (r = 0.258, p = 0.027) during TMST. But a positive link with parasympathetic activity: RMSSD (r = 0.253, p = 0.029) and SDNN (r = 0.269, p = 0.020) **Conclusion**: the findings unveil a triangular relationship, where body fat percentage significantly impacts physical fitness and cardiac autonomic activity during exercise, while a greater sympathetic activity correlates with higher physical fitness. Additionally, physical fitness moderates the link between body fat and cardiac autonomic activity, emphasizing its importance for older adults' health. Further research is needed to explore psychological variables' moderating effects.

@@

81 community-dwelling older adults were recruited and selected by non-probabilistic sampling, from the Region of Magallanes and Chilean Antartica, Chile. They were included if: 65 years age or older; residents of the Region of Magallanes and Chilean Antartica, Chile; and being able to understand the study aims and instructions. But they were excluded in case of: diagnosis of congenital heart disease; consumption of beta-blocker drugs, taking stimulant substances within 24 h before assessments session; motor or cognitive disability; inability to understand instructions or written content; or presence of pain during cardiac or physical assessments.

@@

In addition to the potential strengths of this cross-sectional study, it is not without limitations. In first place, our study design prevents us from making objective inferences about the direction of the relationships, highlighting the relevance of longitudinal research exploring causal relations between our variables and underlying mechanisms. In second place, a relatively small sample was included, limiting generalizability and statistical power of the analysis. Furthermore, the sample consisted mainly of women (82.7%), limiting our ability to make sex comparisons and decreasing the representativeness of the sample. It should also be noted that the relationships between physical fitness and cardiac autonomic response to exercise were not made within the same instrument, due to the possible lack of SPPB to generate an adequate physical stress, and of TMST to inform general physical fitness of the participants. Further research could investigate the impact of cardiac autonomic response on performance during the same task, in this age group.
